The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
review 1

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George}
\IEEEauthorblockA{ECE Paris\\
lgeorge@ece.fr}
\and
\IEEEauthorblockN{Jo\e"l Goossens}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
joel.goossens@ulb.ac.be}
}
\maketitle

\begin{abstract}
Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
conditions  in the case of small changes in task parameters, such as when porting a system to a
different platform. The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
set of execution times for which a system is feasible. This paper extends previous works to
generalize the description of the C-space for Earliest Deadline First scheduling to
systems with initial offset. The feasibility gain offered by offsets is then
expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
synchronous system.
\end{abstract}

@@

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible. A
	precise and efficient description of the C-space of a system would allow to quickly decide
	whether or not it is feasible on a given platform.

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
	sometimes sufficient to consider and we give a numerical example.

@@

\section{Related works}
\label{sct:relatedWorks}
	\subsection{Model}

		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

>>>>

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George}
\IEEEauthorblockA{ECE Paris\\
lgeorge@ece.fr}
\and
\IEEEauthorblockN{Jo\"el Goossens}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
joel.goossens@ulb.ac.be}
}

\maketitle

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as when porting a system to a
	different platform. The C-space describes the
	set of execution times for which a system is feasible. This paper extends previous works to
	generalize the description of the C-space for Earliest Deadline First scheduling to
	systems with initial task offsets. The feasibility gain offered by offsets is
	then expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
	synchronous system.
\end{abstract}

@@

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible
	\cite{bini2004schedulability,george2009characterization}. A precise and efficient description of the C-space of a system would allow to quickly decide
	whether or not it is feasible on a given platform.

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the demand bound function test. Then we show why applying this
	test on the interval starting at $t_d$
	and spanning an hyperperiod when $t_d$ exists is sufficient. A
	numerical example is also given.

@@

\section{Related works}
\label{sct:relatedWorks}
	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).
